Transfer Learning in Visual and Relational Reasoning

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Reworked Figure 1, 6.

% \begin{figure}[!t]
% 	\centering
% 	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
% 	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
% 	\label{fig:clevr-baseline-compare}
% \end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue / yellow (striped)) and fine-tuning on CoGenT-B (gray (dotted)).}
	\label{fig:CoGenT-B-results}
\end{figure}

>>>>

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
	\label{fig:clevr-baseline-compare}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A and fine-tuning on CoGenT-B.}
	\label{fig:CoGenT-B-results}
\end{figure}
